%-------------------------
% Resume in Latex
% Author : Daniil Bederdinov
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{calc} % added
\usepackage{ragged2e}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    \begin{minipage}[t]{0.99\linewidth} % Adjust the width as needed
      {#1}
    \end{minipage}
    \vspace{-2pt} % Adjust the space between elements as needed
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheadingLeftOneRow}[2]{% % added
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
\end{description}
}

\newcommand{\resumeSubSubheadingLeftTwoRows}[4]{%
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
    \item[\small #3]{\textit{\small  #4}}
\end{description}
}

\newcommand{\projectDescription}[1]{
    \vspace{8pt} % Adjust the space between elements as needed
    \small {#1}
    \vspace{-6pt} % Adjust the space between elements as needed
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \small\textbf{\Huge \scshape Daniil Bederdinov} \\ \vspace{1pt}
    \href{mailto:daniil.bederdinov.dev@gmail.com}{\underline{daniil.bederdinov.dev@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/daniil-bederdinov}{\underline{linkedin.com/in/daniil-bederdinov}} $|$
    \href{https://github.com/Palidos}{\underline{github.com/Palidos}} $|$
    \href{https://t.me/bederdinov}{\underline{t.me/bederdinov}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
    \small
        {React and TypeScript Developer with over 6 years of experience in the industry. I am proficient in keeping up with the latest web technologies and promoting a better developer experience. My experience includes cross-browser development, adaptive/responsive design, unit testing and code review also I have mentored newcomers and developed a design system. I hold an advanced English certificate (CAE) and am passionate about alpine skiing. I am now seeking a challenging position where I can utilize my skills and experience to develop innovative web solutions.}
  
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: JavaScript, TypeScript} \\
      \textbf{Frameworks}{: React, Next.JS, Svelte} \\
      \textbf{Technologies and Libraries}{: Express, Redux, Zustand, Tan Stack Query (React query), Jest, React Testing Library, Playwright, Styled-Components, SCSS, MUI, AntDesign, Webpack, Vite}\\
    }}
  \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

     \resumeSubheading
      {Senior Frontend Developer}{Feb 2025 -- Present}
      {FxPro}{Limassol, Cyprus}

    \projectDescription
  {Orchestration of FxPro main website and marketing landing pages, focusing on performance, SEO, modern frontend architecture, and user experience.}
  
    \resumeItemListStart
      \resumeItem{Drastically improved SEO, increasing visibility and organic traffic}
      \resumeItem{Led the transition from legacy Angular architecture to React}
      \resumeItem{Initiated and contributed to shared UI Kit development}
      \resumeItem{Created complex, responsive layouts for marketing and product pages}
      \resumeItem{Improved overall UX through iterative design and frontend enhancements}
      \resumeItem{Spoke at internal technical meetups, sharing knowledge and best practices}
      \resumeItem{Conducted technical interviews}
    \resumeItemListEnd

    \resumeSubheading
      {Senior Frontend Developer}{May 2021 -- Feb 2025}
      {Sber}{Moscow, Russia}

    \projectDescription
      {HR platform that helps to manage all sorts of HR tasks (vacation, remote work, sick-leave, etc.), interact with colleagues (posts, comments, likes, social circle, etc.), monitor employees (risk of dismissal, haven't taken a vacation for a long time, team stats, etc.) and many more.}
        
      \resumeItemListStart
        \resumeItem{Led the transition to a widget system in monorepo, enhancing developer experience and reducing time to production}
        \resumeItem{Boosted IE11 performance for over 85,000 users}
        \resumeItem{Achieved 99\% code coverage across all applications}
        \resumeItem{Enhanced accessibility for key components}
        \resumeItem{Scaled legacy code to support 50x more load}
        \resumeItem{Participated in development of a UI Kit}
        \resumeItem{Conducted interviews}
        \resumeItem{Mentored newcomers}
      \resumeItemListEnd

    \resumeSubheading
      {Frontend Developer}{Aug. 2020 -- Apr. 2021}
      {EORA}{Remote, Russia}

    \projectDescription
      {Interactive fairy tale that can be controlled with a remote control as well as with a voice. Communication between Frontend and Backend was via WebSocket. The device that connected to the TV was equipped with low-performance hardware. Thus, it was crucial to optimize images, videos and animations on the screen.}

      \resumeItemListStart
        \resumeItem{Streamlined media files for optimal performance on low-end hardware}
        \resumeItem{Conducted performance profiling on low-performance devices}
        \resumeItem{Implemented internationalization features}
        \resumeItem{Contributed to the development of a UI Kit}
      \resumeItemListEnd

    \resumeSubheading
    {Frontend Developer}{Sep. 2019 -- Jun. 2020}
    {Artezio}{Nizhny Novgorod, Russia}
    
    \projectDescription
      {Platform with google-like calendar for lesson arrangement, lesson material storage, lesson planning, personal dashboard.}

    \resumeItemListStart
      \resumeItem{Enhanced performance of a google calendar-like page}
      \resumeItem{Refined date manipulation processes}
      \resumeItem{Improved client API Developer Experience by reducing boilerplate code}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RUT Russian University of Transport }{Sep. 2020 -- Jun. 2023}
      {Master of Science in Applied Informatics}{Moscow, Russia}
    \resumeSubheading
      {UNN University of Nizhniy Novgorod}{Sep. 2016 -- Jun. 2020}
      {Bachelor of Science in Software Engineering}{Nizhny Novgorod, Russia}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
